The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2013-05-14 ms.tex
Update ms.tex

% USAGE INSTRUCTIONS:
% Get more information about latex package by using Terminal command   texdoc <packagename> 
% for example: texdoc rotating     or     texdoc aastex    or texdoc titling
% or visit this website: http://www.texdoc.net/   and search for the packagename
% TeXstudio 2.5.2 (SVN 3733M) binary works a lot better and is more stable than texmaker in Ubuntu 13.04
% Build procedure in TeXstudio 2.5.2 (SVN 3733M) (DO NOT USE texmaker):
% 1) OPTIONAL: press Tools:Clean within texstudio to delete old output files
% 2) press F1 to build and view output PDF
% and to correctly compile this .tex file into a valid .PDF output file.
% always save graphics files in f<sequence-number>.PDF format, not in .JPG or .PNG format
% The titling package offers features to create sophisticated title pages.
% The tocbibind package can automatically add bibliography, index, TOC, LOF, and LOT to the table
% of contents. It's even capable of using numbered headings instead of the default
% unnumbered ones.
% Use \citep[page 23]{kennedy1998cationic}  for example when citing bibliography references contained in the .bib 
% bibtex file
% Other handy URL's:
% http://detexify.kirelabs.org/classify.html
% http://www.ottobib.com/
% http://scholar.google.be

@@

% \RequirePackage[l2tabu, orthodox]{nag}

@@

%\usepackage{amsmath}
%\usepackage[a4paper]{geometry}
%\usepackage{graphicx}
%\usepackage{microtype}
%\usepackage{siunitx}
%\usepackage{booktabs}
%\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}
%\usepackage{cleveref}

@@

Figure \ref{fig:Coverage} shows the coverage of the \bgps.  The survey
is contiguous over the range $-10.5 \le \lon \le 90.5, |b| \le 0.5$.
Towards the Cygnus X spiral arm, the coverage was flared to $|b| \le
1.5$ for $75.5 \le \lon \le 87.5$.  In addition, cross-cuts to $|b|
\le 1.5$ were made at $\lon = 3, 15, 30$ and 31.  The total area of
this section is 133 square degrees.  With the exception of the
increase in latitude, no pre-selection criteria were applied to the
coverage in this region.  In addition to the contiguous region, four
targeted regions in the outer Galaxy were observed: IC1396 (9 square
degrees, $97.5 \le \lon \le 100.5$, $2.25 \le b \le 5.25$), a region
towards the Perseus Arm (4 square degrees centered on $\lon = 111$,
$b=0$ near NGC7538), W3/4/5 (18 square degrees, $132.5 \le l \le
138.5$) and Gem OB1 (6 square degrees, $187.5 \le l \le 193.5$).  The
total area of good coverage for the BGPS is \bgpsarea\ square degrees.

@@

Because the Bolocam detector beams do not fully overlap on the sky, if
the array is scanned along detector rows, gaps will be left in the
resulting map.  To ameliorate this, we began using in Epoch II a field
rotator to adjust the rotation angle of the array with respect to the
scan direction so that as the scan proceeded the full extent of the
FOV in the direction orthogonal to the scan was sampled by at least
one detector.  This is shown in Figure \ref{fig:Array}.  Achieving a
uniform sampling along the scan-orthogonal direction is further
complicated by a number of missing bolometers.  A simulation was
performed to determine the optimal angle to rotate the array with
respect to the scan direction to account for both the effects of the
beam spacing and missing bolometers.  During the turnaround following
a raster, the field rotator is adjusted to this optimum angle for the
subsequent raster.  Without the field rotator, the coverage shows
variations of 100\% from pixel to pixel in a single raster of a field.
With the rotator, this is reduced to $\sim40\%$.

@@

\subsection{Point Spread Function, Aperture Corrections,
and Surface Brightness Calibration}

>>>>

% USAGE INSTRUCTIONS:
% Get more information about latex package by using Terminal command   texdoc <packagename> 
% for example: texdoc rotating     or     texdoc aastex    or texdoc titling
% or visit this website: http://www.texdoc.net/   and search for the packagename
% TeXstudio 2.5.2 (SVN 3733M) binary works a lot better and is more stable than texmaker in Ubuntu 13.04
% Build procedure in TeXstudio 2.5.2 (SVN 3733M) (DO NOT USE texmaker):
% 1) OPTIONAL: press Tools:Clean within texstudio to delete old output files
% 2) press F1 to build and view output PDF
% and to correctly compile this .tex file into a valid .PDF output file.
% always save graphics files in f<sequence-number>.PDF format, not in .JPG or .PNG format

% The tocbibind package can automatically add bibliography, index, TOC, LOF, and LOT to the table
% of contents. It's even capable of using numbered headings instead of the default
% unnumbered ones.

% Use \citep[page 23]{kennedy1998cationic}  for example when citing bibliography references contained in the .bib 
% bibtex file
% Use Figure \ref{fig:Array} on page \pageref{fig:Array} for example when referring to a figure at the end of the
% document

% Other handy URL's:
% http://detexify.kirelabs.org/classify.html
% http://www.ottobib.com/
% http://scholar.google.be

@@

\RequirePackage[l2tabu, orthodox]{nag}

@@

\usepackage{amsmath}
\usepackage[a4paper]{geometry}
\usepackage{graphicx}
\usepackage{microtype}
%\usepackage{siunitx}
\usepackage{booktabs}
%\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}
\usepackage{cleveref}

@@

Figure \ref{fig:Coverage} on page \pageref{fig:Coverage} shows the coverage of the \bgps.  The survey
is contiguous over the range $-10.5 \le \lon \le 90.5, |b| \le 0.5$.
Towards the Cygnus X spiral arm, the coverage was flared to $|b| \le
1.5$ for $75.5 \le \lon \le 87.5$.  In addition, cross-cuts to $|b|
\le 1.5$ were made at $\lon = 3, 15, 30$ and 31.  The total area of
this section is 133 square degrees.  With the exception of the
increase in latitude, no pre-selection criteria were applied to the
coverage in this region.  In addition to the contiguous region, four
targeted regions in the outer Galaxy were observed: IC1396 (9 square
degrees, $97.5 \le \lon \le 100.5$, $2.25 \le b \le 5.25$), a region
towards the Perseus Arm (4 square degrees centered on $\lon = 111$,
$b=0$ near NGC7538), W3/4/5 (18 square degrees, $132.5 \le l \le
138.5$) and Gem OB1 (6 square degrees, $187.5 \le l \le 193.5$).  The
total area of good coverage for the BGPS is \bgpsarea\ square degrees.

@@

Because the Bolocam detector beams do not fully overlap on the sky, if
the array is scanned along detector rows, gaps will be left in the
resulting map.  To ameliorate this, we began using in Epoch II a field
rotator to adjust the rotation angle of the array with respect to the
scan direction so that as the scan proceeded the full extent of the
FOV in the direction orthogonal to the scan was sampled by at least
one detector.  This is shown in Figure \ref{fig:Array} on page \pageref{fig:Array}.  
Achieving a uniform sampling along the scan-orthogonal direction is further
complicated by a number of missing bolometers.  A simulation was
performed to determine the optimal angle to rotate the array with
respect to the scan direction to account for both the effects of the
beam spacing and missing bolometers.  During the turnaround following
a raster, the field rotator is adjusted to this optimum angle for the
subsequent raster.  Without the field rotator, the coverage shows
variations of 100\% from pixel to pixel in a single raster of a field.
With the rotator, this is reduced to $\sim40\%$.

@@

\subsection{Point Spread Function, Aperture Corrections,and Surface Brightness Calibration}
\label{sec:PointSpreadFunction}
